On the link between functional traits and growth rate: meta-analysis shows effects change with plant size, as predicted

### 2015-09-02 MS.tex
Format for BES journals
Formatting files kindly provided by Rich FitzJohn

\documentclass[a4paper]{article}\usepackage[]{graphicx}\usepackage[]{color}
\usepackage{alltt}
\usepackage{amssymb,amsmath}
\usepackage{palatino}
\usepackage{framed}
\usepackage{parskip}
\usepackage{graphicx}
\usepackage{fixltx2e}
\usepackage[default,osfigures,scale=0.95]{opensans}
\usepackage{geometry}
\usepackage{longtable}
\usepackage{authblk}
\usepackage[colorinlistoftodos]{todonotes}
\geometry{verbose,tmargin=2cm,bmargin=2cm,lmargin=2cm,rmargin=2.5cm}
\linespread{2}
\usepackage{color}

\usepackage[title,titletoc,toc]{appendix}

\usepackage{etoolbox}
\newbool{MyRefNumbers}
\booltrue{MyRefNumbers}

\usepackage{natbib}

\bibliographystyle{ecol_let}
\setcitestyle{authoryear,open={(},close={)}}
\newcommand{\bibstar}{* }

\begin{document}

\title{On the link between functional traits and growth rate: meta-analysis shows effects change with plant size, as predicted}

\author[1]{Anais Gibert*}
\author[1]{Emma F. Gray}
\author[1]{Mark Westoby}
\author[1]{Ian J. Wright}
\author[1]{Daniel S. Falster}
\affil[1]{Biological Sciences, Macquarie University NSW 2109, Australia}

\maketitle

\textit{Running title (36/45 characters)}Influence of traits on growth changes with size

\textit{Corresponding author} Anais Gibert, anais.gibert@gmail.com, Biological Sciences, Macquarie University NSW 2109, Australia, tel: +61 2 9850 8194

\section*{Abstract (195/350 words)}\label{abstract}

\begin{enumerate}

\item
Growth rates (GR) have often been seen as central elements of plant ecological strategies, and as linked to species traits. Yet, the literature is inconsistent about empirical correlations between functional traits and plant growth rate, casting doubt on the capacity of traits to predict growth.

@@

\textit{Keywords (8/10)} asymptotic maximum height, maximum photosynthetic rate, plant ontogenetic stage, plant functional traits, plant growth strategy, seed mass, specific leaf area, wood density

@@

All analyses were conducted with R software \citep{Ralanguageanden:2014wf}. The code and data for producing all figures and results in this paper is available at github.com/AnaisGibert/Growth\_trait\_metaanalysis.

@@

\begin{figure}[h!]
\centering
\includegraphics{output/Fig1.pdf}
\caption{Number of recorded correlations between trait and growth rate in our dataset, byt size and trait. Results shown here are for the ``complete'' dataset (recorded both across and within species, under unstressed and stressed conditions). Traits are: Aarea (or Amass) = rate of CO$_{2}$ assimilation per unit leaf area (or leaf mass) = maximum photosynthetic rate, Hmax = asymptotic maximum height,  Ks = stem hydraulic conductance, LA = leaf area, LMR = leaf mass ratio, NARarea (or NARmass) = net mass assimilation rate per unit of leaf area (or leaf mass), Nmass (or Narea) = nitrogen content per unit of leaf mass (or leaf area), Pmass = phosphorus content per unit of leaf mass, SA/LA = sapwood area per leaf area, SLA = specific leaf area, thickness = leaf thickness, Vessel size = stem conduit size, vessel density = stem conduit density, WD = wood density.}
\label{fig:fig1}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics{output/Fig2.pdf}
\caption{The range of plant sizes and stage recoded in original publications, compared to standardised thresholds used in the analysis. Panels are for
\textbf{a)} age, \textbf{b)} height and \textbf{c)} diameter. Line segments indicate the size range (max., min.) for the plants used to measure growth. Article IDs correspond to the reference number in our dataset. Colours denote stage information given by the authors, while line styles denote growth form. The vertical lines indicate the thresholds used in our analysis. Results shown here are the ``complete'' dataset (see methods for details).}
\label{fig:fig2}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics{output/Fig3.pdf}
\caption{The relationship between growth rates and traits changes with plant stage and trait. Plots show the effect size (+ 95\%CI) for the average correlation across species, by plant stage. Effect size is a standardized measure of the deviation of correlation coefficient from zero (Fisher's z-transformed). Effects are significant if confidence intervals (95\%CI) for a given stage do not overlap with zero. Results shown are from both the ``complete'' (black)  and ``ideal'' (grey) datasets. Trait names as in Fig. \ref{fig:fig1}. $n$ indicates number of correlations contributing to each effect. Likelihood Ratio Tests (LRT, for ``ideal'' dataset only) compared maximum-likelihood fits between a pooled model and one separated by stage. A significant p-value means the model including stage effect fitted the data better than the null model.
}
\label{fig:fig3}
\end{figure}

\clearpage
\section*{Table}
\setcounter{table}{0}
\begin{table}[h!]
\centering
\caption{\textbf{Hypothesised effects of traits on key elements of plant function determining growth rate.} Arrows indicate the effect an increase in trait value would have on the main elements of growth eqs. \ref{eq:eq0}-\ref{eq:eq4} in Appendix \ref{sec:growth}. Traits are SLA: Specific leaf area, WD: Wood density, Hmax: Asymptotic maximum height, SM: seed mass, Aarea: Maximum photosynthetic rate. For further details, see  Appendix \ref{sec:growth}.}
\vspace{1cm}
  \begin{tabular}{cccc}
   & Leaf deployment per mass & Allocation to vegetative growth & Net live biomass production \\
   Trait
    & ($\frac{\textrm{d}a_\textrm{l}}{\textrm{d}m_\textrm{t}}$)
    & ($\frac{\textrm{d}m_\textrm{t}}{\textrm{d}b}$)
    & ($\frac{\textrm{d}b}{\textrm{d}t}$) \\ \hline
  SLA &$\nearrow$ &$\_$ & $\searrow$  \\
  WD & $\searrow$ &$\_$  &$\_$ \\
  Hmax &$\_$ &$\nearrow$ &$\_$ \\
  SM &$\_$&$\_$&$\_$ \\
  Aarea &$\_$ &$\_$ & $\nearrow$ \\
\hline
  \end{tabular}
\label{tab:trade-offs}
  \end{table}

@@

@@

@@

\clearpage
\begin{appendices}\label{sec:appendices}
\renewcommand{\thefigure}{S\arabic{figure}}
\renewcommand{\thetable}{S\arabic{table}}

@@

\begin{table}[h!]
\centering
\caption{\textbf{List of the twenty traits targeted}. Abbreviation,
definition and search term used in the meta-analysis}
\label{tab:lit_search}
\vspace{0.5cm}
\begin{tabular}{p{3cm}p{3cm}p{8cm}}
  \hline
Trait & Definition & Search terms \\
  \hline
Aarea & Photosynthetic rate per area & ``photosynthetic rate per area'' OR ``rate of CO2 assimilation per area'' OR ``Aarea'' OR ``Amax'' OR ``photosynthetic capacity per area'' \\
  Amass & Photosynthetic rate per mass & ``photosynthetic rate per mass'' OR ``rate of CO2 assimilation per mass'' OR ``Amass'' OR ``Amax'' \\
  Hmax & Maximum height & ``potential height'' OR ``maximum height'' OR ``Hmax'' \\
  Ks & Stem specific conductance & ``Ks'' OR ``stem specific conductance'' OR ``stem hydraulic conductance'' OR ``sapwood conductance'' \\
  LA & Leaf lamina area & ``leaf length'' OR ``leaf lamina area'' OR ``leaf width'' OR ``leaf size'' \\
  LAR & Leaf area ratio & ``leaf area ratio'' \\
  LMR & Leaf mass ratio & ``leaf mass ratio'' OR ``leaf mass fraction'' \\
  NARarea & Net assimilation rate per area &  ``net assimilation rate per area'' OR ``rate of dry mass increament per area'' OR ``NARarea'' OR ``NAR'' \\
  Narea & Leaf nitrogen content per area & ``Narea'' OR ``nitrogen per area'' OR ``N/area'' OR ``leaf nitrogen content per area'' OR ``LNCarea'' OR ``leaf nitrogen content" \\
  NARmass & Net assimilation rate per mass &  ``net assimilation rate per mass'' OR ``rate of dry mass increament per mass'' OR ``NARmass'' OR ``NAR'' \\
  Nmass & Leaf nitrogen content per mass & ``Nmass'' OR ``nitrogen per mass'' OR ``N/mass'' OR ``leaf nitrogen content per mass'' OR ``LNCmass'' OR ``leaf nitrogen content" \\
  Parea & Leaf phosphorus content per area & ``Parea'' OR ``leaf P'' OR  ``leaf phosphorus content per area''  OR ``leaf phosphorus content'' \\
  Pmass & Leaf phosphorus content per mass & ``Pmass'' OR ``leaf P'' OR  ``leaf phosphorus content per mass'' OR ``leaf phosphorus content'' \\
  SA/LA & Sapwood area per leaf area & ``sapwood area per leaf area'' OR ``huber value'' OR ``leaf area per sapwood area'' \\
  Seed mass & Seed mass & ``seed mass'' OR ``seed size'' OR ``seed volume'' \\
  SLA & Specific Leaf Area & ``leaf mass per area'' OR ``specific leaf area'' OR ``leaf construction cost'' \\
  Thickness & Leaf thickness & ``leaf thickness''  OR ``leaf tissue density'' \\
  Vessel density & Vessel density & ``vessel density'' OR ``stem conduit density'' \\
  Vessel size & Vessel area or diameter & ``conduit area'' OR ``stem conduit area'' OR ``vessel diameter'' OR ``vessel size'' OR ``conduit size''   \\
  WD & Wood density & ``wood density'' OR``WD'' OR ``wood specific gravity'' OR ``stem density'' OR ``stem specific density'' OR ``SSD'' \\
   \hline
\end{tabular}
\end{table}

@@

\begin{figure}[h!]
\centering
\includegraphics{output/FigA1.pdf}
\caption{Allometric relationships between a) age and diameter (m), b) age and height (m), and c) diameter and height in trees according to the BAAD database. Green and red lines are the cutoffs between stage categories used in the literature. Green lines corresponds to limits between juveniles and saplings, red lines to limits between saplings and adults.}
\label{fig:figA1}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics{output/FigA2.pdf}
\caption{Geographical distribution of site locations from studies performed in the field used in the meta-analysis. Results shown here are from the ``complete'' dataset (see methods for details).}
\label{fig:figA2}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics{output/FigA3.pdf}
\caption{Range of correlations (r) between
growth and trait reported in the literature (112 articles). Plots shown the coefficients of correlation (r)
between the plant growth and \textbf{a)} Specific leaf area (SLA, n =
111), \textbf{b)} Wood density (WD, n = 64), \textbf{c)} Asymptotic
maximum height (Hmax, n = 23), \textbf{d)} Seed mass (Seedmass, n = 36 and
\textbf{e)} Rate of CO2 assimilation (Aarea, n = 24) reported from 112
articles. The x abcissa represents the articles ID sorted by the average coefficient value r reported.
Results shown here are from the ``complete'' dataset (recorded both across and within species
and under unstressed and stressed conditions). Each bubble represents a r value, the diameter of the bubble
is proportional to its weights in the meta-analysis (i.e. number of species used). The colors
correspond to the stage for which the r values have been recorded: red
points corresponds adult stage, orange points to saplings, and grey
points to juveniles.}
\label{fig:figA3}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics{output/FigA4.pdf}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics{output/FigA4b.pdf}
\caption{\textbf{Mean coefficient correlation r (+SD) between growth rate and traits, established from 112 articles.} The mean coefficients are weighted by sample size (i.e number of species used to perform the correlation), and calculated both across all plant stages and for each stage. Each panel corresponds to a functional trait: \textbf{a)} Specific leaf area (SLA), \textbf{b)} Wood density (WD), \textbf{c)} Net assimilation rate (NARarea), \textbf{d)} Seed mass, \textbf{e)} Asymptotic height (Hmax) and \textbf{f)} Assimilation rate of CO2 (Aarea). Results shown here are from the ``unstressed dataset'' (recorded across species and under unstressed conditions).}
\label{fig:figA4}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics{output/FigA5.pdf}
\caption{\textbf{Effect size (+ 95\%CI) of plant stage on the correlations between growth rate and five functional traits across species, with a data set averaging multiple comparisons by trait and by study.} Effects size are calculated from a reduced dataset; in the case of multiple comparisons within a study, we calculated the mean correlation coefficient by trait and by study. a) Specific leaf area (SLA), b) Wood density (WD), c) Net assimilation rate (NARarea), d) Seed mass, e) Asymptotic height (Hmax) and f) Assimilation rate of CO2 (Aarea). Effect size is a standardized measure of the magnitude of the relationship between a particular stage and the correlation coefficient z (Fisher's z-transformed). Effects are significant if confidence intervals (+CI95\%) do not overlap with zero. LRT: likelihood Ratio Test compared the fit between null model and stage model, both models are fitted by Maximum Likelihood. Black point: ideal data (under unstressed conditions), grey points: all the data. ``n'' indicate the number of independent comparisons for each effect.}
\label{fig:figA5}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics{output/FigA6a.pdf}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics{output/FigA6b.pdf}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics{output/FigA6c.pdf}
\caption{\textbf{Effects size on the correlation between growth and traits of plant stage (mod1), vegetation type (mod2), growth measurement (mod3) and experiment type (mod4).} The effect size (z + 95\%CI) is reported for each class, and models are fitted by restricted max likelihood (REML). n = number of correlation r reported. Abbreviation: across veg = more than 2 vegetation types, boreal\&temp = boreal and temperate deciduous forest, med = Mediterranean,  temp\&med = temperate deciduous and Mediterranean forests, temp = temperate deciduous, temp rain = temperate rain, trop rain = tropical rain, trop seas = tropical seasonal forests, GR = growth rate and RGR = relative growth rate, measured in diameter (D), height (H), mass(M), cross section area (CSA). AIC: Akaike information criterion corresponds to the quality of each model, and allow a comparison between models. Smallest is the AIC better is the model. Results shown here are from ``ideal'' dataset (recorded at interspecific and under unstressed condition) and ``complete'' dataset (recorded at both interspecific and intraspecific level and under unstressed and stressed conditions).}
\label{fig:figA6}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics{output/FigA7.pdf}
\caption{\textbf{Funnel plots with filled in data based on the trim and fill method, showing transformed correlation coefficient z between growth and the traits a) Specific leaf area (SLA), b) Wood density (WD), c) Asymptotic height (Hmax), d) Seed mass (SM) and e) Assimilation rate of CO2 (Aarea)}. Results shown here are from the ``ideal'' dataset (recorded across species and under unstressed conditions).  Note that in these plots the y axis is the 1/number of species included in the correlation, not the replication for the correlation. The number of species is sometimes as low as 1, and these are within-species correlations. The number of replicates used for the correlation coefficient was often much greater than the number of species. Nevertheless, the characteristic shape of funnel plots is observed, with correlations involving few species showing much wider variation even though within-species replication was sometimes high. The open points correspond to the estimated missing studies. The number of missing values is 9 for SLA,1 for WD, 0 for Hmax, 6 for SM and 0 for Aarea}
\label{fig:figA7}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics{output/FigA8.pdf}
\caption{\textbf{Growth measurement used by traits and by size.} Results shown here are from the ``complete'' dataset (recorded across species and under both unstressed and stressed conditions). The colours correspond to the stage for which the r values have been recorded: red bars corresponds adult stage, orange bars to saplings, and grey bars to juveniles.}
\label{fig:figA8}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics{output/FigA9.pdf}
\caption{\textbf{Temporal changes in coefficient of correlation between traits and growth. a) Specific leaf area (SLA), b) Wood density (WD), c) Asymptotic height (Hmax), d) Seed mass (SM) and e) Assimilation rate of CO2 (Aarea)} Results shown here are from the ``ideal'' dataset (recorded across species and under  unstressed conditions). The colours correspond to the stage for which the r values have been recorded: red points corresponds adult stage, orange points to saplings, and grey points to juveniles.}
\label{fig:figA9}
\end{figure}

>>>>

\documentclass[a4paper,11pt]{article}
\usepackage[osf]{mathpazo}
\usepackage{ms}
\usepackage[]{natbib}
\raggedright

\newcommand{\smurl}[1]{{\footnotesize\url{#1}}}
\usepackage{graphicx}
\usepackage[title,titletoc,toc]{appendix}

\title{On the link between functional traits and growth rate: meta-analysis shows effects change with plant size, as predicted}
\author{Anais Gibert\textasteriskcentered, Emma F. Gray, Mark Westoby, Ian J. Wright, Daniel S. Falster}
\affiliation{Biological Sciences, Macquarie University NSW 2109, Australia\\
\textasteriskcentered Email for correspondence: \texttt{ anais.gibert@gmail.com}\\
Word count: ~XXXX words}
\date{}

\bibliographystyle{mee}
\newcommand{\bibstar}{* }

\mstype{Research Article}
\runninghead{Influence of traits on growth changes with size}
\keywords{maximum height, photosynthetic rate, ontogenetic stage, functional trait, growth strategy, seed mass, specific leaf area, wood density}

\begin{document}
\mstitlepage
\noindent
\parindent=1.5em
\addtolength{\parskip}{.3em}
\doublespacing
\linenumbers
\section{Summary}\label{abstract}
\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\itemsep1pt\parskip0pt\parsep0pt
\item Growth rates (GR) have often been seen as central elements of plant ecological strategies, and as linked to species traits. Yet, the literature is inconsistent about empirical correlations between functional traits and plant growth rate, casting doubt on the capacity of traits to predict growth.

@@

@@

All analyses were conducted with R software \citep{Ralanguageanden:2014wf}. The code and data for producing all figures and results in this paper is available at \smurl{github.com/AnaisGibert/Growth\_trait\_metaanalysis}.

@@

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/Fig1.pdf}
\caption{Number of recorded correlations between trait and growth rate in our dataset, byt size and trait. Results shown here are for the ``complete'' dataset (recorded both across and within species, under unstressed and stressed conditions). Traits are: Aarea (or Amass) = rate of CO$_{2}$ assimilation per unit leaf area (or leaf mass) = maximum photosynthetic rate, Hmax = asymptotic maximum height,  Ks = stem hydraulic conductance, LA = leaf area, LMR = leaf mass ratio, NARarea (or NARmass) = net mass assimilation rate per unit of leaf area (or leaf mass), Nmass (or Narea) = nitrogen content per unit of leaf mass (or leaf area), Pmass = phosphorus content per unit of leaf mass, SA/LA = sapwood area per leaf area, SLA = specific leaf area, thickness = leaf thickness, Vessel size = stem conduit size, vessel density = stem conduit density, WD = wood density.}
\label{fig:fig1}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/Fig2.pdf}
\caption{The range of plant sizes and stage recoded in original publications, compared to standardised thresholds used in the analysis. Panels are for
\textbf{a)} age, \textbf{b)} height and \textbf{c)} diameter. Line segments indicate the size range (max., min.) for the plants used to measure growth. Article IDs correspond to the reference number in our dataset. Colours denote stage information given by the authors, while line styles denote growth form. The vertical lines indicate the thresholds used in our analysis. Results shown here are the ``complete'' dataset (see methods for details).}
\label{fig:fig2}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/Fig3.pdf}
\caption{The relationship between growth rates and traits changes with plant stage and trait. Plots show the effect size (+ 95\%CI) for the average correlation across species, by plant stage. Effect size is a standardized measure of the deviation of correlation coefficient from zero (Fisher's z-transformed). Effects are significant if confidence intervals (95\%CI) for a given stage do not overlap with zero. Results shown are from both the ``complete'' (black)  and ``ideal'' (grey) datasets. Trait names as in Fig. \ref{fig:fig1}. $n$ indicates number of correlations contributing to each effect. Likelihood Ratio Tests (LRT, for ``ideal'' dataset only) compared maximum-likelihood fits between a pooled model and one separated by stage. A significant p-value means the model including stage effect fitted the data better than the null model.
}
\label{fig:fig3}
\end{figure}

\clearpage
\section*{Table}
\setcounter{table}{0}
\begin{table}[h!]
\centering
\caption{\textbf{Hypothesised effects of traits on key elements of plant function determining growth rate.} Arrows indicate the effect an increase in trait value would have on the main elements of growth eqs. \ref{eq:eq0}-\ref{eq:eq4} in Appendix \ref{sec:growth}. Traits are SLA: Specific leaf area, WD: Wood density, Hmax: Asymptotic maximum height, SM: seed mass, Aarea: Maximum photosynthetic rate. For further details, see  Appendix \ref{sec:growth}.}
{\footnotesize
\vspace{1cm}
  \begin{tabular}{cccc}
   & Leaf deployment per mass & Allocation to vegetative growth & Net live biomass production \\
   Trait
    & ($\frac{\textrm{d}a_\textrm{l}}{\textrm{d}m_\textrm{t}}$)
    & ($\frac{\textrm{d}m_\textrm{t}}{\textrm{d}b}$)
    & ($\frac{\textrm{d}b}{\textrm{d}t}$) \\ \hline
  SLA &$\nearrow$ &$\_$ & $\searrow$  \\
  WD & $\searrow$ &$\_$  &$\_$ \\
  Hmax &$\_$ &$\nearrow$ &$\_$ \\
  SM &$\_$&$\_$&$\_$ \\
  Aarea &$\_$ &$\_$ & $\nearrow$ \\
\hline
  \end{tabular}
  }
\label{tab:trade-offs}
  \end{table}

@@

{\footnotesize

@@

}

@@

\clearpage
\setcounter{secnumdepth}{1}
\begin{appendices}\label{sec:appendices}
\renewcommand{\thefigure}{S\arabic{figure}}
\renewcommand{\thetable}{S\arabic{table}}

@@

\begin{table}[h!]
\centering
\caption{\textbf{List of the twenty traits targeted}. Abbreviation,
definition and search term used in the meta-analysis}
\label{tab:lit_search}
\vspace{0.5cm}
{\footnotesize
\begin{tabular}{p{3cm}p{3cm}p{8cm}}
  \hline
Trait & Definition & Search terms \\
  \hline
Aarea & Photosynthetic rate per area & ``photosynthetic rate per area'' OR ``rate of CO2 assimilation per area'' OR ``Aarea'' OR ``Amax'' OR ``photosynthetic capacity per area'' \\
  Amass & Photosynthetic rate per mass & ``photosynthetic rate per mass'' OR ``rate of CO2 assimilation per mass'' OR ``Amass'' OR ``Amax'' \\
  Hmax & Maximum height & ``potential height'' OR ``maximum height'' OR ``Hmax'' \\
  Ks & Stem specific conductance & ``Ks'' OR ``stem specific conductance'' OR ``stem hydraulic conductance'' OR ``sapwood conductance'' \\
  LA & Leaf lamina area & ``leaf length'' OR ``leaf lamina area'' OR ``leaf width'' OR ``leaf size'' \\
  LAR & Leaf area ratio & ``leaf area ratio'' \\
  LMR & Leaf mass ratio & ``leaf mass ratio'' OR ``leaf mass fraction'' \\
  NARarea & Net assimilation rate per area &  ``net assimilation rate per area'' OR ``rate of dry mass increament per area'' OR ``NARarea'' OR ``NAR'' \\
  Narea & Leaf nitrogen content per area & ``Narea'' OR ``nitrogen per area'' OR ``N/area'' OR ``leaf nitrogen content per area'' OR ``LNCarea'' OR ``leaf nitrogen content" \\
  NARmass & Net assimilation rate per mass &  ``net assimilation rate per mass'' OR ``rate of dry mass increament per mass'' OR ``NARmass'' OR ``NAR'' \\
  Nmass & Leaf nitrogen content per mass & ``Nmass'' OR ``nitrogen per mass'' OR ``N/mass'' OR ``leaf nitrogen content per mass'' OR ``LNCmass'' OR ``leaf nitrogen content" \\
  Parea & Leaf phosphorus content per area & ``Parea'' OR ``leaf P'' OR  ``leaf phosphorus content per area''  OR ``leaf phosphorus content'' \\
  Pmass & Leaf phosphorus content per mass & ``Pmass'' OR ``leaf P'' OR  ``leaf phosphorus content per mass'' OR ``leaf phosphorus content'' \\
  SA/LA & Sapwood area per leaf area & ``sapwood area per leaf area'' OR ``huber value'' OR ``leaf area per sapwood area'' \\
  Seed mass & Seed mass & ``seed mass'' OR ``seed size'' OR ``seed volume'' \\
  SLA & Specific Leaf Area & ``leaf mass per area'' OR ``specific leaf area'' OR ``leaf construction cost'' \\
  Thickness & Leaf thickness & ``leaf thickness''  OR ``leaf tissue density'' \\
  Vessel density & Vessel density & ``vessel density'' OR ``stem conduit density'' \\
  Vessel size & Vessel area or diameter & ``conduit area'' OR ``stem conduit area'' OR ``vessel diameter'' OR ``vessel size'' OR ``conduit size''   \\
  WD & Wood density & ``wood density'' OR``WD'' OR ``wood specific gravity'' OR ``stem density'' OR ``stem specific density'' OR ``SSD'' \\
   \hline
\end{tabular}
}
\end{table}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA1.pdf}
\caption{Allometric relationships between a) age and diameter (m), b) age and height (m), and c) diameter and height in trees according to the BAAD database. Green and red lines are the cutoffs between stage categories used in the literature. Green lines corresponds to limits between juveniles and saplings, red lines to limits between saplings and adults.}
\label{fig:figA1}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA2.pdf}
\caption{Geographical distribution of site locations from studies performed in the field used in the meta-analysis. Results shown here are from the ``complete'' dataset (see methods for details).}
\label{fig:figA2}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA3.pdf}
\caption{Range of correlations (r) between
growth and trait reported in the literature (112 articles). Plots shown the coefficients of correlation (r)
between the plant growth and \textbf{a)} Specific leaf area (SLA, n =
111), \textbf{b)} Wood density (WD, n = 64), \textbf{c)} Asymptotic
maximum height (Hmax, n = 23), \textbf{d)} Seed mass (Seedmass, n = 36 and
\textbf{e)} Rate of CO2 assimilation (Aarea, n = 24) reported from 112
articles. The x abcissa represents the articles ID sorted by the average coefficient value r reported.
Results shown here are from the ``complete'' dataset (recorded both across and within species
and under unstressed and stressed conditions). Each bubble represents a r value, the diameter of the bubble
is proportional to its weights in the meta-analysis (i.e. number of species used). The colors
correspond to the stage for which the r values have been recorded: red
points corresponds adult stage, orange points to saplings, and grey
points to juveniles.}
\label{fig:figA3}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA4.pdf}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA4b.pdf}
\caption{\textbf{Mean coefficient correlation r (+SD) between growth rate and traits, established from 112 articles.} The mean coefficients are weighted by sample size (i.e number of species used to perform the correlation), and calculated both across all plant stages and for each stage. Each panel corresponds to a functional trait: \textbf{a)} Specific leaf area (SLA), \textbf{b)} Wood density (WD), \textbf{c)} Net assimilation rate (NARarea), \textbf{d)} Seed mass, \textbf{e)} Asymptotic height (Hmax) and \textbf{f)} Assimilation rate of CO2 (Aarea). Results shown here are from the ``unstressed dataset'' (recorded across species and under unstressed conditions).}
\label{fig:figA4}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA5.pdf}
\caption{\textbf{Effect size (+ 95\%CI) of plant stage on the correlations between growth rate and five functional traits across species, with a data set averaging multiple comparisons by trait and by study.} Effects size are calculated from a reduced dataset; in the case of multiple comparisons within a study, we calculated the mean correlation coefficient by trait and by study. a) Specific leaf area (SLA), b) Wood density (WD), c) Net assimilation rate (NARarea), d) Seed mass, e) Asymptotic height (Hmax) and f) Assimilation rate of CO2 (Aarea). Effect size is a standardized measure of the magnitude of the relationship between a particular stage and the correlation coefficient z (Fisher's z-transformed). Effects are significant if confidence intervals (+CI95\%) do not overlap with zero. LRT: likelihood Ratio Test compared the fit between null model and stage model, both models are fitted by Maximum Likelihood. Black point: ideal data (under unstressed conditions), grey points: all the data. ``n'' indicate the number of independent comparisons for each effect.}
\label{fig:figA5}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA6a.pdf}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA6b.pdf}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA6c.pdf}
\caption{\textbf{Effects size on the correlation between growth and traits of plant stage (mod1), vegetation type (mod2), growth measurement (mod3) and experiment type (mod4).} The effect size (z + 95\%CI) is reported for each class, and models are fitted by restricted max likelihood (REML). n = number of correlation r reported. Abbreviation: across veg = more than 2 vegetation types, boreal\&temp = boreal and temperate deciduous forest, med = Mediterranean,  temp\&med = temperate deciduous and Mediterranean forests, temp = temperate deciduous, temp rain = temperate rain, trop rain = tropical rain, trop seas = tropical seasonal forests, GR = growth rate and RGR = relative growth rate, measured in diameter (D), height (H), mass(M), cross section area (CSA). AIC: Akaike information criterion corresponds to the quality of each model, and allow a comparison between models. Smallest is the AIC better is the model. Results shown here are from ``ideal'' dataset (recorded at interspecific and under unstressed condition) and ``complete'' dataset (recorded at both interspecific and intraspecific level and under unstressed and stressed conditions).}
\label{fig:figA6}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA7.pdf}
\caption{\textbf{Funnel plots with filled in data based on the trim and fill method, showing transformed correlation coefficient z between growth and the traits a) Specific leaf area (SLA), b) Wood density (WD), c) Asymptotic height (Hmax), d) Seed mass (SM) and e) Assimilation rate of CO2 (Aarea)}. Results shown here are from the ``ideal'' dataset (recorded across species and under unstressed conditions).  Note that in these plots the y axis is the 1/number of species included in the correlation, not the replication for the correlation. The number of species is sometimes as low as 1, and these are within-species correlations. The number of replicates used for the correlation coefficient was often much greater than the number of species. Nevertheless, the characteristic shape of funnel plots is observed, with correlations involving few species showing much wider variation even though within-species replication was sometimes high. The open points correspond to the estimated missing studies. The number of missing values is 9 for SLA,1 for WD, 0 for Hmax, 6 for SM and 0 for Aarea}
\label{fig:figA7}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA8.pdf}
\caption{\textbf{Growth measurement used by traits and by size.} Results shown here are from the ``complete'' dataset (recorded across species and under both unstressed and stressed conditions). The colours correspond to the stage for which the r values have been recorded: red bars corresponds adult stage, orange bars to saplings, and grey bars to juveniles.}
\label{fig:figA8}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA9.pdf}
\caption{\textbf{Temporal changes in coefficient of correlation between traits and growth. a) Specific leaf area (SLA), b) Wood density (WD), c) Asymptotic height (Hmax), d) Seed mass (SM) and e) Assimilation rate of CO2 (Aarea)} Results shown here are from the ``ideal'' dataset (recorded across species and under  unstressed conditions). The colours correspond to the stage for which the r values have been recorded: red points corresponds adult stage, orange points to saplings, and grey points to juveniles.}
\label{fig:figA9}
\end{figure}
